---
title: "Analysis Of Fund zhanbo"
author: "Wu Wei"
date: "2017-9-7"
output: html_document
---



## 1 Library input & Data Input
```{r, eval=TRUE}
rm(list = ls())

suppressMessages(library(forecast))
suppressMessages(library(ggplot2))
suppressMessages(library(rugarch))
suppressMessages(library(lmtest))
suppressMessages(library(tseries))
suppressMessages(library(fBasics))
suppressMessages(library(car))
suppressMessages(library(FinTS))
suppressMessages(library(grid))
suppressMessages(library(gridExtra))
suppressMessages(library(vars))
```

```{r source, echo = FALSE}
source("d://MyR//dongfanghong//ComputeMarketModel.R")
source("d://MyR//dongfanghong//ComputeTMModel.R")
source("d://MyR//dongfanghong//ComputeHMModel.R")
source("d://MyR//dongfanghong//panel_cor.R")

source("d://MyR//zhao//CreateTSPYearMonthLabel.r")

source("d://MyR//stock//CompareObjectAccuracy.R")
source("d://MyR//stock//CompareObjectNaiveAccuracy.R")

source("d://MyR//stock//CompareObjectZeroDiffAccuracy.R")
```

```{r, eval=TRUE}
setwd("d://MyR//zhanbo//")
zhanbo.original.data <- read.csv("zhanbomonthlyjingzhi.csv")
# (original.data)

zhanbo.close.price <- ts(zhanbo.original.data[,2], start = c(2009, 6 ), frequency = 12)
names(zhanbo.close.price) <- as.character(zhanbo.original.data[,1])

money.interest <- ts(zhanbo.original.data[,3], start = c(2009, 6 ), frequency = 12)
hushen300.price <- ts(zhanbo.original.data[,4], start = c(2009, 6 ), frequency = 12)
zz500.price <- ts(zhanbo.original.data[,5], start = c(2009, 6 ), frequency = 12)
zz800.price <- ts(zhanbo.original.data[,6], start = c(2009, 6 ), frequency = 12)

jinglin.price <- ts(zhanbo.original.data[,7], start = c(2009, 6 ), frequency = 12)
szhl.price <- ts(zhanbo.original.data[,8], start = c(2009, 6 ), frequency = 12)
```

```{r}
zhanbo.monthly.return <- ts(diff(log(zhanbo.close.price)), start = c(2009,7), frequency = 12)

hushen300.monthly.return <- diff(log(hushen300.price))

zz500.monthly.return <- diff(log(zz500.price))

zz800.monthly.return <- diff(log(zz800.price))

jinglin.monthly.return <- diff(log(jinglin.price))

szhl.monthly.return <- diff(log(szhl.price))

money.monthly.interest <- ts(log(1 + (money.interest[-1] / 12)),start = c(2009,7), frequency = 12)

```

```{r}
hushen300.monthly.return.no.risk <- ts(round(as.numeric(hushen300.monthly.return - money.monthly.interest) * 100, 
                                              digits = 2), 
                                       start = c(2009,7), frequency = 12)

zz500.monthly.return.no.risk <- ts(round(as.numeric(zz500.monthly.return - money.monthly.interest) * 100, 
                                              digits = 2), 
                                       start = c(2009,7), frequency = 12)

zz800.monthly.return.no.risk <- ts(round(as.numeric(zz800.monthly.return - money.monthly.interest) * 100, 
                                              digits = 2), 
                                       start = c(2009,7), frequency = 12)

zhanbo.monthly.return.no.risk <- ts(round(as.numeric((zhanbo.monthly.return - money.monthly.interest) * 100),
                                     digits = 2),start = c(2009,7), frequency = 12)

jinglin.monthly.return.no.risk <- ts(round(as.numeric((jinglin.monthly.return - money.monthly.interest) * 100),
                                     digits = 2),start = c(2009,7), frequency = 12)

szhl.monthly.return.no.risk <- ts(round(as.numeric((szhl.monthly.return - money.monthly.interest) * 100),
                                     digits = 2),start = c(2009,7), frequency = 12)

```

```{r}
cor(zhanbo.monthly.return.no.risk, jinglin.monthly.return.no.risk)
```



```{r}
zhanbo.yearly.return <- diff(log(zhanbo.close.price), lag = 12)
```


## 2 Analysis for monthly return
```{r, eval=TRUE}


plot(zhanbo.monthly.return, type = "l")

abline(h = 0, col = "red")
```

```{r, eval=TRUE}

ndiffs(zhanbo.monthly.return)

```

```{r, fig.height=8, fig.width=10}

tsdisplay(zhanbo.monthly.return)

```



```{r, eval=TRUE}
# mean(zhanbo.monthly.return)
# 
# mean(zhanbo.monthly.return) * 12
# 
# sd(zhanbo.monthly.return)
# 
# sd(zhanbo.monthly.return) * sqrt(12)
# 
# quantile(zhanbo.monthly.return, c(0.05, seq(0,1,0.25)))

skewness(zhanbo.monthly.return)
kurtosis(zhanbo.monthly.return)
jarqueberaTest(zhanbo.monthly.return)


```


```{r main 2.7,  fig.height=3, fig.width=8, echo=FALSE}

d <- 
data.frame("从2009年至今的月收益均值" = paste0(round(mean(hushen300.monthly.return)*100,digits = 2),"%"),
                "从2009年至今的月收益波动率" = paste0(round(sd(hushen300.monthly.return)*100,digits = 2),"%"),
                "从2009年至今的月收益下限" = paste0(round(quantile(hushen300.monthly.return, 0.05)*100,digits = 2),"%"),
                "从2009年至今的月收益夏普比例" = round(mean(hushen300.monthly.return.no.risk) / (100 *sd(hushen300.monthly.return)),digits = 2))

row.names(d)[1] <- "沪深300"


d <- rbind(d,
data.frame("从2009年至今的月收益均值" = paste0(round(mean(zz500.monthly.return)*100,digits = 2),"%"),
                "从2009年至今的月收益波动率" = paste0(round(sd(zz500.monthly.return)*100,digits = 2),"%"),
                "从2009年至今的月收益下限" = paste0(round(quantile(zz500.monthly.return, 0.05)*100,digits = 2),"%"),
                "从2009年至今的月收益夏普比例" = round(mean(zz500.monthly.return.no.risk) / (100 *sd(zz500.monthly.return)),digits = 2)))

row.names(d)[2] <- "中证500"

d <- rbind(d,
data.frame("从2009年至今的月收益均值" = paste0(round(mean(zhanbo.monthly.return)*100,digits = 2),"%"),
                "从2009年至今的月收益波动率" = paste0(round(sd(zhanbo.monthly.return)*100,digits = 2),"%"),
                "从2009年至今的月收益下限" = paste0(round(quantile(zhanbo.monthly.return, 0.05)*100,digits = 2),"%"),
                "从2009年至今的月收益夏普比例" = round(mean(zhanbo.monthly.return.no.risk) / (100 *sd(zhanbo.monthly.return)),digits = 2)))

row.names(d)[3] <- "展博一期"

d <- rbind(d,
data.frame("从2009年至今的月收益均值" = paste0(round(mean(jinglin.monthly.return)*100,digits = 2),"%"),
                "从2009年至今的月收益波动率" = paste0(round(sd(jinglin.monthly.return)*100,digits = 2),"%"),
                "从2009年至今的月收益下限" = paste0(round(quantile(jinglin.monthly.return, 0.05)*100,digits = 2),"%"),
                "从2009年至今的月收益夏普比例" = round(mean(jinglin.monthly.return.no.risk) / (100 *sd(jinglin.monthly.return)),digits = 2)))

row.names(d)[4] <- "景林稳健"

d <- rbind(d,
data.frame("从2009年至今的月收益均值" = paste0(round(mean(szhl.monthly.return)*100,digits = 2),"%"),
                "从2009年至今的月收益波动率" = paste0(round(sd(szhl.monthly.return)*100,digits = 2),"%"),
                "从2009年至今的月收益下限" = paste0(round(quantile(szhl.monthly.return, 0.05)*100,digits = 2),"%"),
                "从2009年至今的月收益夏普比例" = round(mean(szhl.monthly.return.no.risk) / (100 *sd(jinglin.monthly.return)),digits = 2)))

row.names(d)[5] <- "深证红利"


g <- tableGrob(t(d))
grid.newpage()
grid.draw(g)
```




## 3.  Analysis of monthly return between zhanbo and hushen300 with money interest subtracted

### 3.1 Analysis of total data


```{r}
# cor(hushen300.monthly.return.no.risk, zhanbo.monthly.return.no.risk)

# cor(data.frame(hushen300 = as.numeric(hushen300.monthly.return.no.risk), 
#                  zz500 = as.numeric(zz500.monthly.return.no.risk),
#                  szhl = as.numeric(szhl.monthly.return.no.risk)))

```

```{r, fig.height=7, fig.width=9}

pairs(data.frame(zhanbo = as.numeric(zhanbo.monthly.return.no.risk),
                 hushen300 = as.numeric(hushen300.monthly.return.no.risk), 
                 zz500 = as.numeric(zz500.monthly.return.no.risk)),
      upper.panel = panel.cor)
```



```{r}
fit.4 <- lm(zhanbo.monthly.return.no.risk ~ zz500.monthly.return.no.risk)

fit.5 <- lm(zhanbo.monthly.return.no.risk ~ hushen300.monthly.return.no.risk + zz500.monthly.return.no.risk)

anova(fit.4, fit.5)
```

```{r}

fit.6 <- lm(zhanbo.monthly.return.no.risk ~ zz800.monthly.return.no.risk)

```

```{r}
fit.8 <- lm(zhanbo.monthly.return.no.risk ~ hushen300.monthly.return.no.risk)

```


```{r}
summary(fit.4)
summary(fit.6)
summary(fit.8)
```



```{r, fig.height=6, fig.width=8}
plot(fit.4, which = 1)
plot(fit.4, which = 2)


sort(round(hatvalues(fit.4), 3))

sort(round(dfbetas(fit.4)[,2], 3))

```



```{r, fig.height=6, fig.width=8}
plot(as.numeric(zz500.monthly.return.no.risk), 
     as.numeric(zhanbo.monthly.return.no.risk), 
     type = "p", 
     xlab = "中证500月度超额收益率%", 
     ylab = "展博1期月度超额收益率%", 
     main = "证券特征线")

abline(h = 0, v = 0, col = "green")
points(tail(zz500.monthly.return.no.risk), tail(zhanbo.monthly.return.no.risk), col = "purple", pch = 20)

abline(fit.4)

```

### 3.1.1 Analysis of total data using TM model
```{r}
zz500.monthly.return.square <- zz500.monthly.return.no.risk^2

fit.tm <- lm(zhanbo.monthly.return.no.risk ~ zz500.monthly.return.no.risk + 
                     zz500.monthly.return.square)

summary(fit.tm)
```

### 3.1.2 Analysis of total data using HM model
```{r}

zz500.monthly.return.positive <- zz500.monthly.return.no.risk
zz500.monthly.return.positive[zz500.monthly.return.positive < 0] <- 0

fit.hm <- lm(zhanbo.monthly.return.no.risk ~ zz500.monthly.return.no.risk + 
                     zz500.monthly.return.positive)

summary(fit.hm)
```

### 3.2 Analysis of moving 12 months data

```{r}
alpha <- ts(rep(0,length(zhanbo.monthly.return.no.risk)), start = c(2009,7), frequency = 12)
beta <- alpha
gamma <- alpha

return.matrix.tm <- cbind(zhanbo.monthly.return.no.risk, 
                       zz500.monthly.return.no.risk, 
                       alpha, 
                       beta,
                       gamma) 

dimnames(return.matrix.tm)[[2]][1] <- "zhanbo"
dimnames(return.matrix.tm)[[2]][2] <- "zz500"

return.matrix.hm <- return.matrix.tm

return.matrix <- return.matrix.tm[,1:4]
```

```{r}
return.matrix <- ComputeMarketModel(return.matrix)

window(return.matrix, start = c(2017,1))
```

```{r, fig.height=18, fig.width=10}


start.time <- tsp(return.matrix)[1]
end.time <- tsp(return.matrix)[2]
month.interval <- 1

result.tsp.label <- CreateTSPYearMonthLabel(start.time, end.time, month.interval)

x.axis.grid.points <- result.tsp.label[, "x.axis.grid.points"]
x.axis.grid.labels <- result.tsp.label[, "x.axis.grid.labels"]


```


```{r, fig.height=10, fig.width=10}
plot.layout.matrix <- matrix(c(1,2,3), 
                             nr = 3,
                             byrow = TRUE)

layout(plot.layout.matrix)

plot(return.matrix[,"zhanbo"],axes = FALSE,type = "o")
axis(1, at = x.axis.grid.points, labels = x.axis.grid.labels)
axis(2, las = 1)
abline(v = x.axis.grid.points, col = "grey", lty = "dotted")
abline(h = 0, col = "green")


plot(return.matrix[,"alpha"],axes = FALSE,type = "o")
axis(1, at = x.axis.grid.points, labels = x.axis.grid.labels)
axis(2, las = 1)
abline(v = x.axis.grid.points, col = "grey", lty = "dotted")
abline(h = 0, col = "green")

plot(return.matrix[,"beta"],axes = FALSE,type = "o")
axis(1, at = x.axis.grid.points, labels = x.axis.grid.labels)
axis(2, las = 1)
abline(v = x.axis.grid.points, col = "grey", lty = "dotted")
abline(h = 0, col = "green")


layout(matrix(1))
```

#### 3.2.1 Analysis of moving 12 months data using TM model


```{r 3.2.1}
return.matrix.tm <- ComputeTMModel(return.matrix.tm)

window(return.matrix.tm, start = c(2017,1))
```

```{r}
fit.alpha <- auto.arima(return.matrix.tm[,"alpha"], d = 0)
estimated.alpha <- forecast(fit.alpha, h = 3)$mean
```


```{r 3.2.2, fig.height=12, fig.width=10}
plot.layout.matrix <- matrix(c(1,2,3,4), 
                             nr = 4,
                             byrow = TRUE)

layout(plot.layout.matrix)


plot(return.matrix.tm[,"zhanbo"],axes = FALSE,type = "o")
axis(1, at = x.axis.grid.points, labels = x.axis.grid.labels)
axis(2, las = 1)
abline(v = x.axis.grid.points, col = "grey", lty = "dotted")
abline(h = 0, col = "green")

plot(return.matrix.tm[,"alpha"],axes = FALSE,type = "o")
lines(estimated.alpha, 
      type = "o", 
      col = "red",
      lwd = 2)

axis(1, at = x.axis.grid.points, labels = x.axis.grid.labels)
axis(2, las = 1)
abline(v = x.axis.grid.points, col = "grey", lty = "dotted")
abline(h = 0, col = "green")

plot(return.matrix.tm[,"beta"],axes = FALSE,type = "o")
axis(1, at = x.axis.grid.points, labels = x.axis.grid.labels)
axis(2, las = 1)
abline(v = x.axis.grid.points, col = "grey", lty = "dotted")
abline(h = 0, col = "green")

plot(return.matrix.tm[,"gamma"],axes = FALSE,type = "o")
axis(1, at = x.axis.grid.points, labels = x.axis.grid.labels)
axis(2, las = 1)
abline(v = x.axis.grid.points, col = "grey", lty = "dotted")
abline(h = 0, col = "green")


layout(matrix(1))
```










#### 3.2.2 Analysis of moving 12 months data using HM model


```{r}
return.matrix.hm <- ComputeHMModel(return.matrix.hm)

window(return.matrix.hm, start = c(2017,1))
```

```{r, fig.height=12, fig.width=10}
plot.layout.matrix <- matrix(c(1,2,3,4), 
                             nr = 4,
                             byrow = TRUE)

layout(plot.layout.matrix)

plot(return.matrix.hm[,"zhanbo"],axes = FALSE,type = "o")
axis(1, at = x.axis.grid.points, labels = x.axis.grid.labels)
axis(2, las = 1)
abline(v = x.axis.grid.points, col = "grey", lty = "dotted")
abline(h = 0, col = "green")

plot(return.matrix.hm[,"alpha"],axes = FALSE,type = "o")
axis(1, at = x.axis.grid.points, labels = x.axis.grid.labels)
axis(2, las = 1)
abline(v = x.axis.grid.points, col = "grey", lty = "dotted")
abline(h = 0, col = "green")

plot(return.matrix.hm[,"beta"],axes = FALSE,type = "o")
axis(1, at = x.axis.grid.points, labels = x.axis.grid.labels)
axis(2, las = 1)
abline(v = x.axis.grid.points, col = "grey", lty = "dotted")
abline(h = 0, col = "green")

plot(return.matrix.hm[,"gamma"],axes = FALSE,type = "o")
axis(1, at = x.axis.grid.points, labels = x.axis.grid.labels)
axis(2, las = 1)
abline(v = x.axis.grid.points, col = "grey", lty = "dotted")
abline(h = 0, col = "green")


layout(matrix(1))
```


## 4 Analysis for yearly return

```{r, eval=TRUE}


plot(zhanbo.yearly.return, type = "l")
abline(h = 0, col = "red")
```

```{r, eval=TRUE}

ndiffs(zhanbo.yearly.return)

```

```{r, fig.height=8, fig.width=10}

tsdisplay(zhanbo.yearly.return)

```


```{r, eval=TRUE}
mean(zhanbo.yearly.return)
sd(zhanbo.yearly.return)

quantile(zhanbo.yearly.return, c(0.05, seq(0,1,0.25)))

tail(zhanbo.yearly.return, 2)

skewness(zhanbo.yearly.return)
kurtosis(zhanbo.yearly.return)
jarqueberaTest(zhanbo.yearly.return)

Acf(zhanbo.yearly.return)
```



